Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-10 main.tex
work on Poincare

\section{Introduction}

@@

We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry. 
In particular, this yields computable upper bounds for Poincar\'e--Friedrichs inequalities. 
For example, if $\bff \in \bfL^{p}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
we want to bound the $L^p$ norm of the potential
\begin{align*}
    \argmin\limits_{ \substack{ \bfv \in \bfL^{p}(\curl) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align*}
Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
We address this topic in the special case where $\Omega$ admits a shellable triangulation.
While this constraints us to the class of {\color{red}contractible} domains, 
having computable upper bounds for such domains is an important step stone towards the more general case. 
For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.

@@

We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
we search for a constant $C > 0$ such that 
\begin{align*}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
Even though the existence of such a bounded linear potential construction is not evident a priori, 
picking the average-free potential 
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
\end{align*}
is known to be a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
\begin{align*}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align*}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities. 
The optimal values for all $1 \leq p < \infty$ are known when the domain is convex.

The situation is less clear cut when we try to find try the curl or divergence operators
\begin{align*}
    \curl : \bfW^{p}(\curl) \rightarrow \bfL^{p}(\curl),
    \quad 
    \divergence : \bfW^{p}(\divergence) \rightarrow L^{p}(\curl),
\end{align*}
where we use the function spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. 
In the Banach space case, it is not immediately evident the kernels of these operators are complemented.
We are interested in constants for inequalities such as 
\begin{align*}
    \argmin\limits_{ \substack{ v \in W^{p}(\curl) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)},
    \leq 
    C_{\curl}
    \| \bff \|_{L^{p}(\Omega)}
    \\
    \argmin\limits_{ \substack{ v \in W^{p}(\divergence) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)},
    \leq 
    C_{\divergence}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norm of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega).
\end{align*}
We notice that not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs for the curl and divergence operators, even if the domain is convex, which is in sharp contrast to the study of the gradient operator. 
In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
\\

@@

By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
The literature is much scarcer when it comes to this. 
We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
By duality, that implies lower bounds for the case of full boundary conditions.
We remark that their work also shows that over convex domains in 3D:
\begin{align*}
    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
\end{align*}
But we need to find potentials over a simplex subject to partial boundary conditions 
and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
has no estimates in the literature.

@@

\section{Basic notions of triangulations}

@@

\section{Constructive estimate of Poincar\'e constants}

@@

\section{Shellable triangulated domains}

@@

% \begin{lemma}
%     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
%     In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ is manifold-like for every $m \geq 0$.
% \end{lemma}
% \begin{proof}    
% \end{proof}

We notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}

@@

    Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold, and suppose that its boundary complex $\partial\calT$ is either empty or strongly connected.  
    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$. In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$. We write $\calT'$ be the  simplicial complex that contains $\calT \cup T$.
    We exclude that case $n \leq 1$ since otherwise the discussion is trivial.

    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
    \begin{align*}
        \begin{CD}
            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
        \end{CD}
    \end{align*}
    We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
    By the nature of the mappings in the Mayer-Vietoris sequence, 
    \color{red}which uses some specific knowledge about the arrows\color{black}, 
    we see that 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0 
        \end{CD}
    \end{align*}
    is an exact sequence. 
    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
    the Mayer-Vietoris sequence includes the exact sequence 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow 0 
        \end{CD}
    \end{align*}
    and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
    Finally, the Mayer-Vietoris sequence includes the exact sequences 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT') \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT') \longrightarrow 0 
        \end{CD}
    \end{align*}
    % Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
    % one easily sees that $H_{0}(\calT') \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
    Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
    In the case that $\calS$ is isomorphic to disk,
    then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T)$ are trivial and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
    Consider now the case that $\calS$ is isomorphic to a sphere.
    Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$. Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq \bbZ$. 
    \color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
    Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.

    We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
    \begin{align*}
        H_0(\calT) \simeq \bbZ, 
        \quad 
        H_1(\calT) \simeq \dots \simeq H_{n-1}(\calT) \simeq 0.
    \end{align*}
    Moreover, $H_n(\calT) \simeq \bbZ$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.

@@

\section{Extension operator on finite element stars}

\section{Constructive estimate of Poincar\'e--Friedrichs constants}

>>>>

\section{Introduction}\label{section:intro}

@@

We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry. 
In particular, this yields computable upper bounds for Poincar\'e--Friedrichs inequalities. 
For example, if $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field over some domain $\Omega \subseteq \bbR^3$, 
we want to bound the $\bfL^2$ norm of the potential
\begin{align*}
    \argmin\limits_{ \substack{ \bfv \in \bfL^{2} \\ \curl \bfv = \bff } } \| \bfv \|_{\bfL^{2}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{\bfL^{2}(\Omega)}
    .
\end{align*}
Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
We address this topic in the special case where $\Omega$ admits a shellable triangulation.
Even though only contractible domains can admit a shellable triangulation, 
having computable upper bounds for such domains is an important step stone towards the more general case. 
For example, local patches around a simplex within a larger triangulation belong to the class of shellable triangulations.

We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
we search for a constant $C > 0$ such that 
\begin{align*}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
Even though the existence of such a bounded linear potential construction is not evident a priori, 
picking the average-free potential 
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
\end{align*}
is a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
\begin{align*}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align*}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.

The situation is less clear cut when we study the curl or divergence operators
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\curl,\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
where we use the function spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
{\color{red}The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. }
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
We are interested in constants for inequalities such as 
\begin{align*}
    \argmin\limits_{ \substack{ v \in W^{p}(\curl,\Omega) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \qquad 
    \argmin\limits_{ \substack{ v \in W^{p}(\divergence,\Omega) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)}
    \leq 
    C_{\divergence}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norm of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}
We remark that seemingly not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators, 
% even if the domain is convex, 
which is in sharp contrast to the study of the gradient operator.

We explore formulate our main results in the framework of exterior calculus.
The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
%
It is used ubiquitiously in physics and engineering. 
%
For the purpose of our discussion, this formalisms allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
\\

Before we outline the main results of this exposition in more details, 
we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains.

% Convex domains

% Domains starshaped wrt ball

% Limitations

Most research on optimal constants has addressed the case of convex domains. 
Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.

In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
\\

@@

@@

By contrast, the construction of curl and divergence potentials needs to repeated solve the potential problem for a vector-valued problem over simplices subject to tangential or normal boundary conditions, respectively, along a part of the boundary.
The literature is much scarcer when it comes to this. 
We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
By duality, that implies lower bounds for the case of full boundary conditions.
We remark that their work also shows that over convex domains in 3D:
\begin{align*}
    C_{\grad,p} \geq C_{\curl} \geq C_{\divergence}.
\end{align*}
But we need to find potentials over a simplex subject to partial boundary conditions 
and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.
Even solving the potential equation of the gradient of a simplex subject to Dirichlet boundary conditions along a single face 
has no estimates in the literature.

An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
We refer to \cite{hurri1988poincare} for that perspective.

@@

The remainder of this manuscript is structured as follows.
We review basic notions of triangulations in Section~\ref{section:triangulations} and provide computable upper bounds for Poincar\'e constants over triangulated domains in Section~\ref{section:poincare}.
We then review the notion of shellable triangulation in Section~\ref{section:shellable}.
We construct an important geometric reflection operator in Section~\ref{section:extension}
and provide computable upper bounds for Poincar\'e--Friedrichs constants over shellable triangulations in Section~\ref{section:poincarefriedrichs}.

\section{Basic notions of triangulations}\label{section:triangulations}

@@

\section{Constructive estimate of Poincar\'e constants}\label{section:poincare}

@@

\section{Shellable triangulated domains}\label{section:shellable}

@@

\begin{lemma}
    If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$ and is non-branching, then it triangulates a manifold, possibly with boundary.
    In particular, $\patch_{\calT}(T_{0}) \cup \patch_{\calT}(T_{1}) \cup \dots \cup \patch_{\calT}(T_{m})$ triangulates a manifold for all $m \geq 0$.
\end{lemma}
\begin{proof}    
\end{proof}

The notion of shelling is taken from Ziegler's book~\cite{ziegler2012lectures}

@@

    Suppose that $\calT$ is a strongly connected $n$-dimensional simplicial complex that triangulates a manifold.
    Suppose that its boundary complex $\partial\calT$ is not empty and strongly connected.  
    We exclude the case $n \leq 1$ since otherwise the discussion is trivial.

    Suppose furthermore that $T$ is an $n$-simplex, $T \notin \calT$, 
    whose boundary complex intersects with $\partial\calT$ at a non-empty simplicial complex $\calS$ of dimension $n-1$. 
    In particular, $\calS$ is either the whole boundary complex of $T$ or a patch around a proper subsimplex of $T$. 
    We write $\calT'$ for the  simplicial complex that contains $\calT \cup T$.
    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
    \begin{align*}
        \begin{CD}
            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
        \end{CD}
    \end{align*}
    We notice that $\calS$, $\calT$, $T$ and $\calT'$ are each connected, and hence their zeroth homology groups are isomorphic to ${G}$. 
    By the nature of the mappings in the Mayer-Vietoris sequence, 
    \color{red}which uses some specific knowledge about the arrows\color{black}, 
    we see that 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT') \longrightarrow 0 
        \end{CD}
    \end{align*}
    is an exact sequence. 
    Moreover, $H_{k}(\calS) = H_{k}(T) = 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
    the Mayer-Vietoris sequence includes the exact sequence 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT') \longrightarrow 0 
        \end{CD}
    \end{align*}
    and we conclude that $H_{k}(\calT) = 0$ for $0 < k < n-1$.
    Finally, the Mayer-Vietoris sequence includes the exact sequence 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT') \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT') \longrightarrow 0 
        \end{CD}
    \end{align*}
    % Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT')$.
    % % We know that  $H_{0}(\calT') \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq {G}$ because the respective simplicial complexes are path-connected. 
    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
    % one easily sees that $H_{0}(\calT') \simeq {G}$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT')$. 
    Since $\calT$ and $T$ are triangulations of manifolds with non-empty boundary, their $n$-th simplicial homology groups vanish. 
    In the case that $\calS$ is isomorphic to disk, we have $H_{n-1}(\calS) = 0$,
    and then $H_{n}(\calT') \simeq H_{n}(\calT \oplus T) = 0$ are trivial 
    and $H_{n-1}(\calT') \simeq H_{n-1}(\calT \oplus T)$ follows.
    Consider now the case that $\calS$ is isomorphic to a sphere.
    Since the boundary complex of $\calT$ is strongly connected and non-branching, it must coincide with $\calS$. Hence $\calT'$ triangulates a manifold without boundary, and thus $H_{n}(\calT') \simeq {G}$. 
    \color{red}By some hand-waving argument, $H_{n}(\calT') \longrightarrow H_{n-1}(\calS)$ is an isomorphism.\color{black}
    Hence $H_{n-1}(\calT) \rightarrow H_{n-1}(\calT')$ is an isomorphism.

    We conclude that the simplicial homology groups of a shellable $n$-dimensional simplicial complex $\calT$ that triangulates a manifold satisfy 
    \begin{align*}
        H_0(\calT) \simeq {G}, 
        \quad 
        H_1(\calT) \simeq \dots \simeq H_{n-1}(\calT) \simeq 0.
    \end{align*}
    Moreover, $H_n(\calT) \simeq {G}$ if $\calT$ has no boundary and $H_n(\calT) \simeq 0$ otherwise.

@@

\section{Extension operator on finite element stars}\label{section:extension}

\section{Constructive estimate of Poincar\'e--Friedrichs constants}\label{section:poincarefriedrichs}
